Redundant calibration as a complex optimization problem

### 2017-01-11 paper.tex
more added to the conclusion

\section{Conclusion}
In Section~\ref{sec:} we showed that instead of using the traditional phase-and-amplitude approach to perform redundant calibration we can actually use a purely complex
framework. In this framework the unknown variables and their conjugates are treated as independent variables that have to be estimated. We have also 
proposed to use the LM algorithm, instead of the GN algorithm, to perform the actual parameter estimation within this complex framework. The LM algorithm exhibits better convergence properties than the 
GN algorithm. This has the immediate consequence that the amount of algorithmic layers that are needed to perform redundant calibration are reduced.
Them most expensive operation associated with the LM algorithm (as well as the GN algorithm) is the inversion of $\bH$.
We also compared the computational complexity of two previously proposed algorithms to efficiently invert $\bH$ for the redundant calibration use case, namely 
ADI and PCG. We showed that the computational complexity of the ADI method is $\mathbb{O}(P)$, while the computational complexity of the PCG method is asymptotically bounded
by $\mathbb{O}(P^2)$. Both of these algorithms perform much better than stock standard inversion, which has a computational complexity of $\mathbb{O}(P^3)$.
Although the ADI method does execute faster than the PCG method it is less robust as it

>>>>

\section{Conclusion}
In Section~\ref{sec:} we showed that instead of using the traditional phase-and-amplitude approach to perform redundant calibration we can actually use a purely complex
framework. In this framework the unknown variables and their conjugates are treated as independent variables that have to be estimated. We have also 
proposed to use the LM algorithm, instead of the GN algorithm, to perform the actual parameter estimation within this complex framework. The LM algorithm exhibits better convergence properties than the 
GN algorithm. This has the immediate consequence that the amount of algorithmic layers that are needed to perform redundant calibration are reduced.
Them most expensive operation associated with the LM algorithm (as well as the GN algorithm) is the inversion of $\bH$.
We also compared the computational complexity of two previously proposed algorithms to efficiently invert $\bH$ for the redundant calibration use case, namely 
ADI and PCG. We showed that the computational complexity of the ADI method is $\mathbb{O}(P)$, while the computational complexity of the PCG method is asymptotically bounded
by $\mathbb{O}(P^2)$. Both of these algorithms perform much better than stock standard inversion, which has a computational complexity of $\mathbb{O}(P^3)$.
Although the ADI method does execute faster than the PCG method it is far less robust as it would be less straightforward to apply to other calibration uses cases. The reason being,
the diagonal approximation we make with might not be accurate
